Towards End-user Web Scraping For Customization

### 2021-02-14 paper.tex

\begin{figure*}
  \includegraphics[width=\textwidth]{media/limitations.png}
  \caption{\label{fig:limitations} Two example pages where our generalization algorithm does not currently work. The elements with the blue border correspond to rows of the data in each layout respectively.}
\end{figure*}

@@

End-user web scraping for customization relates to existing work in
end-user web scraping by a number of tools.

@@

@@

Sifter \citep{huynh2006} is a tool that augments websites with advanced
sorting and filtering functionality. Similarly to Wildcard, it uses web
scraping techniques to extract data from websites in order to enable
customizations. However, Wildcard supports a broader range of
customizations beyond sorting and filtering, including adding
annotations to websites and running computations with a spreadsheet
formula language.

Our scraping tool intentionally provides less automation than Sifter.
Sifter attempts to automatically detect items and fields on the page
with a variety of clever heuristics, including automatically detecting
link tags and considering the size of elements on the page. It then
gives the user the option of correcting the result if the heuristics do
not work properly. In contrast, our heuristics are simpler and make
fewer assumptions about the structure of websites. Rather, we give more
control to the user from the beginning of the process, and incorporate
live feedback to help the user provide useful demonstrations. We
hypothesize that focusing on a tight feedback loop rather than
automation may support a scraping process that is just as fast as an
automated one, but gives the user finer control and extends to a greater
variety of websites where more complex heuristics do not apply. However,
further user testing is required to actually validate this hypothesis.

>>>>

\begin{figure*}
  \includegraphics[width=\textwidth]{media/limitations.png}
  \caption{\label{fig:limitations} Two example pages where our generalization algorithm does not currently work. The elements with the blue border correspond to rows of the data and the elements with green borders correspond to tables of data in each layout respectively. For the layout on the left, sorting could lead to rows from one table ending up in the other. For the layout on the right, sorting would lead to a distortion of the table since the column elements cannot be moved as a unit.}
\end{figure*}

@@

End-user web scraping for customization relates to existing work in
end-user web scraping and end-user web customization by a number of
tools.

\hypertarget{end-user-web-scraping}{%
\subsection{End-user Web Scraping}\label{end-user-web-scraping}}

@@

\hypertarget{end-user-web-customization}{%
\subsection{End-user Web
Customization}\label{end-user-web-customization}}

@@

Sifter \citep{huynh2006} is a tool that augments websites with advanced
sorting and filtering functionality. Similarly to Wildcard, it uses web
scraping techniques to extract data from websites in order to enable
customizations. However, Wildcard supports a broader range of
customizations beyond sorting and filtering, including adding
annotations to websites and running computations with a spreadsheet
formula language. Our scraping tool intentionally provides less
automation than Sifter. Sifter attempts to automatically detect items
and fields on the page with a variety of clever heuristics, including
automatically detecting link tags and considering the size of elements
on the page. It then gives the user the option of correcting the result
if the heuristics do not work properly. In contrast, our heuristics are
simpler and make fewer assumptions about the structure of websites.
Rather, we give more control to the user from the beginning of the
process, and incorporate live feedback to help the user provide useful
demonstrations. We hypothesize that focusing on a tight feedback loop
rather than automation may support a scraping process that is just as
fast as an automated one, but gives the user finer control and extends
to a greater variety of websites where more complex heuristics do not
apply. However, further user testing is required to actually validate
this hypothesis.
